### 2013-06-24 latex/SupportingText.tex
I updated the SupportingText.tex table and included my recalculated results in the recalcResultsDariya.txt

\begin{center}
\footnotesize
\begin{tabular}{lccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & $\phi$ & $\psi$ & & $\phi$ & $\psi$ \\
\hline Alanine & $-51.9^{\circ}$ & $-37.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$ \\
                      &  $-66.7^{\circ}$ & $-13.1^{\circ}$ &  & $-45^{\circ}$& $-40^{\circ}$\\
                      & $-52.1^{\circ}$ & $-33.6^{\circ}$ & & $70^{\circ}$& $-5^{\circ}$\\
                      & $-58.6^{\circ}$ & $-30.7^{\circ}$& &\\
Arginine        & $-79.2^{\circ}$ & $-20.2^{\circ}$ & & $-70^{\circ}$ & $-25^{\circ}$ \\
		 &	&	& & $-70^{\circ}$ & $-5^{\circ}$\\
		 &	&	& & $-60^{\circ}$ & $-15^{\circ}$\\
		 &	&	& & $-55^{\circ}$ & $-30^{\circ}$\\
		 &	&	& & $-40^{\circ}$ & $-50^{\circ}$\\      
Asparagine      & $-74.1^{\circ}$ & $-3.6^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ \\
                    & $-94.8^{\circ}$& $-3.4^{\circ}$& & $-50^{\circ}$ & $-30^{\circ}$\\
		& $-67.4^{\circ}$& $-16.8^{\circ}$& & $70^{\circ}$& $-5^{\circ}$\\
Aspartate    & $-73.0^{\circ}$ & $-11.0^{\circ}$ & & $70^{\circ}$ & $-5^{\circ}$ \\
Cysteine        & $-61.4^{\circ}$ & $-23.4^{\circ}$ & & $-60^{\circ}$ & $-20^{\circ}$ \\
Glutamine      & $-66.8^{\circ}$ & $-20.3^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$  \\
		&	&	& & $70^{\circ}$ & $-5^{\circ}$\\
Glutamate     & $-60.2^{\circ}$ & $-39.6^{\circ}$ & & $-60^{\circ}$ to $-55^{\circ}$ & $-25^{\circ}$ to $-20^{\circ}$ \\
		&      	&	& & $60^{\circ}$ & $15^{\circ}$\\
		&	&	& & $65^{\circ}$ & $5^{\circ}$\\
Glycine          & $76.9^{\circ}$ & $0.7^{\circ}$ & & $-65^{\circ}$ to $-60^{\circ}$ & $-15^{\circ}$ to $-10^{\circ}$  \\
Histidine        & $-93.7^{\circ}$ & $12.9^{\circ}$ & & $-80^{\circ}$ to $-75^{\circ}$ & $130^{\circ}$  \\
		 &	 &	&  & $-80^{\circ}$ & $170^{\circ}$ \\
Isoleucine     & $-64.1^{\circ}$ & $-21.9^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$ \\
		&	&	& & $-50^{\circ}$ & $-40^{\circ}$ \\
Leucine         & $-58.1^{\circ}$ & $-24.8^{\circ}$ & & $-70^{\circ}$ & $-5^{\circ}$  \\
 		&  & & & $55^{\circ}$ & $15^{\circ}$  \\
Lysine           & $-62.1^{\circ}$ & $-24.4^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$ \\
Methionine   & $-67.5^{\circ}$ & $-27.5^{\circ}$ & & $-60^{\circ}$ & $-20^{\circ}$  \\
		&	&	& & $-55^{\circ}$ & $-30^{\circ}$ \\
Phenylalanine  & $-50.3^{\circ}$ & $135.2^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$  \\
Proline &  $-38.3^{\circ}$ & $-57.8^{\circ}$ & & $-55^{\circ}$ & $-20^{\circ}$  \\
		&   &  & & $-40^{\circ}$ & $-50^{\circ}$  \\
Serine          & $-58.1^{\circ}$ & $-27.3^{\circ}$ & & $-60^{\circ}$ to $-55^{\circ}$ & $-25^{\circ}$ to $-15^{\circ}$  \\
		& $-57.5^{\circ}$ & $-36.1^{\circ}$ & & $65^{\circ}$ & $5^{\circ}$  \\
		& $-103.4^{\circ}$ & $1.1^{\circ}$ &  & $70^{\circ}$ & $-5^{\circ}$   \\
Threonine          & $-65.0^{\circ}$ & $-27.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$  \\
		&	&	& & $-45^{\circ}$ & $-45^{\circ}$ \\
Tryptophan          & $-67.6^{\circ}$& $-9.8^{\circ}$ & & $-75^{\circ}$ & $-15^{\circ}$  \\
		&  &  & & $-75^{\circ}$ & $0^{\circ}$  \\
		&  &  & & $-60^{\circ}$ to $-55^{\circ}$ & $-25^{\circ}$ to $-20^{\circ}$ \\
		&  &  & & $-50^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$ \\
Tyrosine          & $-61.7^{\circ}$ & $-32.4^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$ \\
Valine          & $-48.9^{\circ}$ & $-28.0^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$  \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\footnotesize
\begin{tabular}{lccccc}
&  \multicolumn{2}{c}{Empirical} & ~~~& \multicolumn{2}{c}{Theoretical}\\\cline{2-3}\cline{5-6}
Residue & $\phi$ & $\psi$ & & $\phi$ & $\psi$ \\
\hline Alanine & $-51.9^{\circ}$ & $-37.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$ \\
                      &  $-66.7^{\circ}$ & $-13.1^{\circ}$ &  &\\
                      & $-52.1^{\circ}$ & $-33.6^{\circ}$ & &\\
Arginine        & $-79.2^{\circ}$ & $-20.2^{\circ}$ & & $-70^{\circ}$ & $-5^{\circ}$ \\
		 &	&	& & $-70^{\circ}$ & $-25^{\circ}$\\
		 &	&	& & $-60^{\circ}$ & $-15^{\circ}$ to $-10^{\circ}$\\
		 &	&	& & $-55^{\circ}$ & $-30^{\circ}$\\
                 &      &       & & $-40^{\circ}$ & $-50^{\circ}$\\      
Asparagine      & $-94.8^{\circ}$ & $-3.4^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ \\
                 &      &       & & $-50^{\circ}$ & $-30^{\circ}$\\
		 &      &       & & $70^{\circ}$ & $-5^{\circ}$\\
Aspartate    & $-79.4^{\circ}$ & $83.0^{\circ}$ & & $70^{\circ}$ & $-5^{\circ}$ \\
Cysteine        & $-87.7^{\circ}$ & $-45.1^{\circ}$ & & $60^{\circ}$ & $-40^{\circ}$ \\
Glutamine      & $-65.5^{\circ}$ & $-24.0^{\circ}$ & & $70^{\circ}$ & $-5^{\circ}$\\
Glutamate     & $-55.0^{\circ}$ & $-49.9^{\circ}$ & & $-60^{\circ}$ & $-15^{\circ}$\\
Glycine          & $80.2^{\circ}$ & $7.2^{\circ}$ & & $-75^{\circ}$ & $20^{\circ}$  \\
                 &      &       & & $-75^{\circ}$ & $50^{\circ}$\\
                 &      &       & & $-70^{\circ}$ & $0^{\circ}$\\
                 &      &       & & $-65^{\circ}$ & $-10^{\circ}$\\
                 &      &       & & $-60^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $-50^{\circ}$ & $-25^{\circ}$\\
                 &      &       & & $70^{\circ}$ & $-15^{\circ}$\\
                 &      &       & & $75^{\circ}$ & $-30^{\circ}$\\
Histidine        & $51.2^{\circ}$ & $32.4^{\circ}$ & & $-180^{\circ}$ & $155^{\circ}$  \\
		 &	 &	& & $-80^{\circ}$ & $170^{\circ}$ to $175^{\circ}$ \\
                 &       &      & & $-80^{\circ}$ to $-75^{\circ}$ & $130^{\circ}$ \\
Isoleucine      & $-64.1^{\circ}$ & $-21.9^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$ \\
		&	&	& & $-50^{\circ}$ & $-40^{\circ}$ \\
Leucine         & $-55.8^{\circ}$ & $-36.4^{\circ}$ & & $-70^{\circ}$ & $-5^{\circ}$  \\
                & $-63.5^{\circ}$ & $-44.5^{\circ}$ & & & & \\
                & $-60.9^{\circ}$ & $-29.3^{\circ}$ & & & & \\
                & $-81.6^{\circ}$ & $-13.5^{\circ}$ & & & & \\
Lysine          & $63.1^{\circ}$ & $23.1^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$ to $-40^{\circ}$ \\
Methionine      & $-67.5^{\circ}$ & $-27.5^{\circ}$ & & $50^{\circ}$ & $-40^{\circ}$  \\
Phenylalanine   & $-50.3^{\circ}$ & $135.2^{\circ}$ & & $-45^{\circ}$ & $-40^{\circ}$  \\
                &       &       & & $70^{\circ}$ & $-10^{\circ}$ \\
Proline         &  $-63.8^{\circ}$ & $-21.6^{\circ}$ & & $-55^{\circ}$ & $-20^{\circ}$  \\
Serine          & $-58.1^{\circ}$ & $-27.3^{\circ}$ & & $65^{\circ}$ & $-45^{\circ}$ \\
		& $-103.4^{\circ}$ & $1.1^{\circ}$ & & & & \\
Threonine       & $-57.4^{\circ}$ & $-17.3^{\circ}$ & & $-45^{\circ}$ & $-45^{\circ}$  \\
Tryptophan          & $-68.0^{\circ}$ & $-62.3^{\circ}$ & & $65^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$  \\
		&       &       & & $70^{\circ}$ & $-55^{\circ}$  \\
Tyrosine        & $-67.6^{\circ}$ & $-9.8^{\circ}$ & & $-50^{\circ}$ & $-40^{\circ}$ to $-35^{\circ}$ \\
                &       &       & & $-45^{\circ}$ & $-45^{\circ}$
Valine          & $-56.2^{\circ}$ & $-31.7^{\circ}$ & & $-55^{\circ}$ & $-25^{\circ}$  \\
\hline
\end{tabular}
\end{center}
